Unveiling Exception Handling Bug Hazards in Android based on GitHub and Google Code Issues

### 2015-03-29 android-stacks.tex
minor changes on results

\begin{document}
%\title{ What GitHub and Google Code can tell us about the Causes of Crashes of Android Apps? }
%\title{ A Mining Study the Google Code can tell us about the Causes of Crashes of Android Apps? }

%\title{What can the Issues of GitHub and Google Code tell us about Exception Fragilities? }

%\title{What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java? }

@@

%\title{Results of a Mining Study on Exception Stack Traces embedded on issues of over 600 Android Projects}

%\title{Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects}

%\title{Discovering Threats to Robustness through Exception Stack Trace Analysis: Results of a Mining Study of Android Projects}

%\title{Discovering Threats to Robustness through Exception Stack Trace Mining}

%\title{Discovering Threats to Robustness through Exception Stack Trace Mining of over 600 Android Projects}

%\title{Discovering Threats to Robustness through a Mining Study of Exception Stack Traces}

%\title{Discovering Fragilities on the Exception-Related Code through  Exception Stack Trace Mining}

%\title{On the Common Characteristics Android-Apps Crashes: Results of a GitHub and Google Code Mining Study}

%\title{On the Common Characteristics of Android-Apps Crashes: Results of a GitHub and Google Code Mining Study}

%\title{On the Common Characteristics of Android Crashes: Results of a GitHub and Google Code Mining Study}

%\title{A first Glance on Characteristics of Android Crashes: Results of a GitHub and Google Code Mining Study}

%\title{A first Glance on Characteristics of Android Crashes: Results of a GitHub and Google Code Mining Study}

@@

This paper reports on a study mining the exception stack traces included in
159,048 issues reported on Android projects hosted in GitHub (482 projects) 
and Google Code (157 projects). The goal of this study is to investigate 
whether stack trace information can reveal \emph{bug hazards} related to exception handling code that may lead to a decrease in application robustness. 
 Overall 6,005 exception stack traces were extracted, and subjected to source code and bytecode analysis. 
The outcomes of this study include the identification of the following 
\emph{bug hazards}: (i) unexpected cross-type exception wrappings (for instance, trying to handle an instance 
of OutOfMemoryError ``hidden'' in  a checked exception)  which can make the exception-related code 
more complex and negatively impact the application robustness; (ii) undocumented runtime exceptions 
thrown by both the Android platform and third party libraries; and (iii) undocumented checked exceptions
 thrown by the Android Platform. Such undocumented exceptions make difficult, and most of the times infeasible
for the client code to protect against ``unforeseen'' situations that may happen while calling third-party code.
This study provides further insights on such \emph{bug hazards} and the robustness threats  
they impose to Android apps as well as to other systems based on the Java exception model.

%A bug hazard is a circumstance that increases the chance of a bug to be present in the software.
\end{abstract}

@@

This study performs a post mortem analysis of the exception stack traces 
included in issues
reported on Android projects hosted in GitHub and Google Code. 
The goal of this study is to investigate whether the reported exception stack traces
 can reveal common \emph{bug hazards} in the exception-related code.  
A \emph{bug hazard}~\cite{binder2000testing}  is a circumstance that increases the 
chance of a bug to be present in the software. An example of a bug hazard can 
be a characteristic of  the exception-related code which can increase the likelihood 
of introducing the aforementioned uncaught exceptions.

@@

The remainder of this paper is organized as follows. 
Section~\ref{sec:back} provides the necessary
background on the Android platform and Java exception model. 
Section~\ref{sec:study} presents the study design. 
Section~\ref{sec:exceptionminer} describes the ExceptionMiner tool we developed to conduct our study.
Section~\ref{sec:result} reports the findings of our study.
Section~\ref{sec:disc} provides a discussion of the wider implications of our results.
Section~\ref{sec:threats} presents the threats to validity associated to this study. 
Finally Section~\ref{sec:rele} describes related work, 
and Section~\ref{sec:conc} concludes the paper and outlines
directions for future work.

@@

%\begin{figure} \centering \includegraphics[scale=0.8]{arch3.png}
%  \caption{Android Architecture} \label{fig:exchier} \end{figure}

@@

%\begin{figure} \centering \includegraphics[width=\hsize]{new2_hierarchy.png}
% \caption{Exception Hierarchy in Java} \label{fig:exchier} \end{figure}

@@

The goal of our mining study is to explore to what extent exception stack traces 
contained in issues of Android projects (hosted in GitHub and Google Code), can reveal 
\emph{bug hazards} in the exception-related code of both the applications and the underlying framework. 
As mentioned before, in this context \emph{bug hazards} are the characteristics of exception-related code 
that favor the introduction of failures such as uncaught exceptions.

This exploration is guided by the set of best practices covered in Section~\ref{sec:best}.
To support our investigation, we developed a tool called ExceptionMiner (Section~\ref{sec:exceptionminer})
which extracts the exception stack traces embedded on issues, 
and combines stack trace information with source code and bytecode 
analysis. Moreover, we use manual inspection to augment
 the understanding of stack traces and support further discussions and insights (Section~\ref{sec:manual}).
In this study we explore the domain quantitatively and highlight interesting cases by 
exploring cases qualitatively.

@@

\emph{\textbf{Exception Stack Trace Distiller.}}
This component is based on a combination between a parser (based on regular expressions) 
and heuristics able to identify and filter exception names and stack traces inline with text. 
This component distills the information that composes a stack trace.
 Some of the attributes extracted from the stack trace are
 the root exception and its signaler, as well as the exception wrappers and their corresponding signalers. 
This component also distills fine grained information of each attribute such as the classes and packages associated to them.
In contrast to existing issue parsing solutions such as Infozilla, our parser
 can discover stack traces mixed with log file information\footnote{In several 
exception stack traces, the exception frames were preceeded by logging information e.g., 
\texttt{03-01 15:55:01.609 (7924): at android.app.ActivityThread.access\$600(ActivityThread\-.java:127)} which could not be detected by existing tools.}.

\emph{\textbf{Exception Type Analysis.}} To support a deeper investigation of the 
stack traces every exception defined on a stack trace needs to be classified according to its type
(e.g. Error, checked Exception or RuntimeException). The module responsible for this analysis 
uses the Design Wizard framework \cite{Brunet09} to inspect the bytecode of the exceptions reported 
on stack traces.  It walks up the type hierarchy of a Java exception until it reaches 
a base exception type. Hence in this study the bytecode analysis was used to discover the type 
of each mined exception when the jar file of such exception was available on the project or 
on a reused  Java library. An specific implementation (based on source code analysis)
 was needed to discover the exception type when the bytecode was not available.
With this module we analyzed all exceptions defined in the Android platform (Version 4.4, API level 19),
which includes all basic Java exceptions that can be thrown during the app execution,
and exceptions thrown by Android core libraries. Moreover, we also analyzed the 
exceptions reported on stack traces that were defined on applications and third-party libraries 
(the tool only analyzed the last version available).

\emph{\textbf{Exception Signaler Analysis.}}
This module is responsible for classifying each signaler according 
to its origin (i.e., Android Application Framework, Android Libcore, Application, Library). 
Table~\ref{tab:signalers} presents the heuristics adopted in this classification.
To conduct this classification, we provide this module with the information
comprising all Java packages that compose: the Android Plaform;
 the Android Libcore; and each analyzed Application. To discover the packages for the first two origins
we can use to the Android specification.
To discover the packages for the third origin, the application itself, this module
extracts the manifest files of each Android app, which defines the main packages that the applications consist of.
 If this file is not available, the tool recursively analyzes the 
structure of source-code directories composing the appm filtering out the cases in which the application also includes the source code of reused libraries.
Then, based on this information and using pattern matching 
between the signaler name and the packages, this module identifies 
the origin of the exception signalers.

@@

\subsection{Manual Inspections}
\label{sec:manual}
In our experiments, the output of the ExceptionMiner tool was manually extended
in order to 
(i) support the identification of packages composing the Android platform, 
libs and apps analyzed in this study (as described previously); and (ii)  
identify the type of some exceptions reported in issues 
that were not automatically identified by the ExceptionMiner tool
(because they were defined on previous versions of libraries,
apps and Android Plaform). When the exception could not be  
found automatically or manually (because they were defined on a previous version
of the app or lib), we classified the exception as ``Undefined''.  Only 31 exceptions 
remained undefined, which occurred in 60 different exception stack traces (see Table~\ref{tab:typeroottab}).

@@

This section presents the results of the study, this presentation is centered around parts 
of exception stack traces (i.e., the root exceptions, the exception types, 
and the exception wrappings).  Each part is then analyzed in detail to 
check whether they can reveal bug harzards on the exception handling code
related or not to violations of the best practices presented
 in Section~\ref{sec:best}.

\subsection{Can the root exceptions reveal bug harzards?}

After distilling the information available on the exception stack traces, we could find 
the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:topten} presents a list of the top 10 root exceptions found in the study - 
 ranked by the number of distinct projects on which they were reported. 
This table also shows how many times the signaler of such an exception was a method defined on
the Android platform, the Android libcore, the application itself or a third-party library -
 following the classification presented in Table  \ref{tab:signalers}.

@@

%\begin{figure}
%\centering
%\includegraphics[width=\hsize]{top_exceptios_android_new2.pdf}
%\includegraphics[width=\hsize]{top_exceptions_android_new}
%\caption{Top exceptions in Android repositories.}
%\label{fig:androidsignaler}
%\end{figure}

@@

\finding{Almost two thirds of all crashes come from runtime
  exceptions. Most of these originate from the application layer.
Hence, most of the bug hazards are located on this layer.}

@@

\emph{\textbf{Missing Checked Exceptions on Exception Interfaces.}} 
Our exception stack trace analysis revealed an unexpected bug hazard: a 
checked exception thrown by a native method and not declared on the exception 
interface of these methods signaling them. The native method in question was defined in
 the Android platform, which uses Java Native Invocation (JNI) to access 
native C/C++ code. This exception was thrown by the method getDeclaredMethods defined in java.lang.Class. 
The Java-side declaration of this method does not have any throws clause, 
leading programmers and the compiler to think that no checked exceptions can be thrown.
 However, the C-code implementation did throw a ``checked exception" called NoSuchMethodException, 
violating the declaration. The Java compiler could not detect this violation, because it does 
not perform static exception checking on native methods. This type of bug is hard to diagnose
because the developer usually does not have access to the native implementations. 
Consequently, since it is not expected by the programmer, when such method throws 
this exception, such an undocumented exception may remain
uncaught and cause the app to crash, or maybe mistakenly handled by subsumption.
The exception stack traces reporting this scenario actually correspond
to a real bug of Android 
Gingerbread version (which still accounts for 13.6\% of devices running Android).
%Among the Android projects on which this exception stack trace was reported we can cite:
%PageTurner (206 stars), ActionBarSherlock (6,041 stars), otto (1,618
%stars).

@@

\finding{%
A common practice in Android plaform are general catch clauses masking any exception 
into a general RuntimeException - it violates best practice III and is considered a bug 
hazard as it loses contextual information about the exception.
}

@@

On the other hand, the inspection 
also revealed instances of Error wrapping checked exceptions. Such wrappings were 
mostly performed by Java static initializers. If any exception is thrown in the context of a static initializer 
(i.e., static block)  it is converted into an ExceptionInitializerError 
on the point where the class is first used.  Table~\ref{tab:exampeswrap} also illustrates
examples of such wrappings. Although such a wrapping may represent a design decision,
it violates the best practice related to checked exceptions and errors as it mixes the intended handling 
behaviour associated to both types.

@@

%\begin{figure*} \centering \includegraphics[scale=0.55]{examples_new2.png}
%\caption{Code snippets illustrating fragilities on the exception-related code} \label{fig:snippets} \end{figure*}

@@

\emph{External Validity.} Our work uses the GHTorrent dataset, which although 
comprehensive and extensive is not an exact replica of Github. 
However, the result of this study does not depend on the analysis of
a complete Github dataset. Instead, the goal of our study was to 
pinpoint \emph{bug hazards} on the exception-related code based on 
exception stack trace mining of a subset of projects.
We limited our analysis to a subset of existing open-source Android projects.
We are aware that the exception stack traces reported 
for commercial apps can be different from the ones found in this study, and that
this subset is a small percentage of existing apps.
Such threats are similar to the ones imposed to other empirical studies 
which also use free or open-source Android apps~\cite{Linar13,McDon13,Ruiz12}.
Moreover, several exception stack traces that support the findings of this study
refered to exceptions coming from methods defined on Android Application Framework
and third-party libraries.  Additionaly,  the \emph{bug hazards} observed in this study are due to
characteristics of Java exception model, which can impose challenges 
the robustness of not only to Android apps but also to other systems
 based on the same exception model.

@@

\textit{Analysis and Use of Stack Trace Information.} Several papers have
investigated the use of stack trace information to support: bug classification
and clustering~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},
fault prediction models~\cite{kim2013predicting}, automated
bug fixing tools~\cite{sinha2009fault} and also the analysis of Android APIs~\cite{kechagia2014}. 
Kim et al.~\cite{kim2011crash} use an
aggregated form of multiple stack traces available in crash reports to detect
duplicate crash reports and to predict if a given crash will be fixed. Dhaliwal
et al.~\cite{dhaliwal2011classifying} proposed a crash grouping approach that
can reduce bug fixing time in approximately 5\%. Wang et
al.~\cite{wang2013improving} propose an approach to identify correlated crash
types and describe a fault localization method to locate and rank files related
to the bug described on a stack trace. Schroter et al.~\cite{schroter2010stack}
conducted an empirical study on the usefulness of stack traces for bug fixing
and showed that developers fixed the bugs faster when failing stack traces were
included on bug issues.  In a similar study, Bettenburg et
al.~\cite{bettenburg2008makes} identify stack traces as the second most stack
trace feature for developers.  Sinha et al.~\cite{sinha2009fault} proposed an
approach that uses stack traces to guide a dataflow analysis for locating and
repairing faults that are caused by the implicitly signaled exceptions. Kim
at al.~\cite{kim2013predicting} proposed an approach to predict the
crash-proneness of methods based information extracted from stack traces and
methods' bytecode operations.  They observed that most of the stack traces were
related to NullPointerException and other implicitly thrown exceptions had
the higher prevalence on the analyzed set of stacks. Kechagia and Spinellis~\cite{kechagia2014}
examined the stack traces embedded on crash reports sent by 1,800 Android apps 
to a crash report management service (i.e., BugSense). They found that 19\% of such stack traces
were caused by unchecked and undocumented exceptions thrown by methods defined on 
Android API (level 15). Our work differs from Kechagia and Spinellis since it is not based on
stack traces mined from issues reported by open source developers on GitHub and Googlecode.  
Moreover, our study mapped the origin of each exception 
(i.e., libraries, the Android platform or the application itself) and investigated
the adoption of best practices based on the analysis of stack trace information.
Our work also identified the type of each exception mined from issues
(classifying them as Error, Runtime or Checked) based on the source code
analysis of the exception hierarchy and analized the exception wrappings that can 
happen during the exception propagation.  Such analysis revealed intrigging 
\emph{bug hazards} such as the cross-type exception wrappings not discussed in previous works.

@@

\textit{Empirical Studies on Exception Handling Defects.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source code of 32 open-source systems, both for Java and .NET. They
observed that the actions inside handlers were very simple (e.g., logging and present a
message to the user). Coelho et al.~\cite{coelho2008assessing} performed an 
empirical study considering the fault-proneness of aspect-oriented implementations 
for handling exceptions. Two releases of both Java and AspectJ implementations were 
assessed as part of that study. Based on the use of an exception
flow analysis tool, the study revealed that the AOP  refactoring increased the 
number of uncaught exceptions, degrading the robustness of the AO version of every analyzed system.
The main limitation of approaches based static analysis based approaches are the number of false
positives they can generate, and the problems the faced when dealing with reflection libraries 
and dynamic class loading. Pingyu and Elbaum~\cite{Zhang12} were the first to perform
an empirical investigation of issues, related to exception-related bugs, on Android projects.  
They perform a small scale study on which they manually inspected the issues of 
5 Android applications. They observed that 29\% had to do with poor
exceptional handling code, this empirical study was used to motivate the development of a tool
aiming at amplifying existing tests to validate exception 
handling code associated with external resources. This work inspired ours,
 which automaticaly mined the exception stack traces embedded on issues 
reported on 639 open source Android projects. The goal of our study was
to identify common \emph{bug hazards} on the exception related code that can lead to 
failures such as uncaught exceptions.

\textit{Empirical studies using Android apps.} Ruiz et al.~\cite{Ruiz12}
investigated the degree of reuse across applications in Android Market, the
study showed that almost 23\% of the classes inherited from a base class in the
Android API, and that 217 mobile apps were reused completely by another mobile
app. Pathak et al.~\cite{Patha11} analyzed bug reports and developers
discussions of Android platform and found out that approximately 20\% of
energy-related bugs in Android occurred after an OS update. McDonnell et
al.~\cite{McDon13} conducted a case study of the co-evolution behavior of
Android API and 10 dependent applications using the version history data found
in GitHub. The study found that approximately 25\% of all methods in the client
code used the Android API, and that the methods reusing fast-evolving APIs were
more defect prone then others. Vásquez et al.~\cite{Linar13} analyzed
approximately 7K free Android apps and observed that the last successful apps
used Android APIs that were on average 300\% more change-prone than the APIs
used by the most successful apps. Our work differs from the others as it aims at
distilling stack trace information of bug reports and combine such information
with bytecode analysis, source code analysis and manual inspections
to identify \emph{bug hazards} on the exception handling code of Android apps.

>>>>

\begin{document}

@@

@@

This paper reports on a study mining the exception stack traces included in
159,048 issues reported on Android projects hosted in GitHub (482 projects) 
and Google Code (157 projects). The goal of this study is to investigate 
whether stack trace information can reveal \emph{bug hazards} related to exception handling code that may lead to a decrease in application robustness. 
 Overall 6,005 exception stack traces were extracted, and subjected to source code and bytecode analysis. 
The outcomes of this study include the identification of the following 
\emph{bug hazards}: (i) unexpected cross-type exception wrappings (for instance, trying to handle an instance 
of OutOfMemoryError ``hidden'' in  a checked exception)  which can make the exception-related code 
more complex and negatively impact the application robustness; (ii) undocumented runtime exceptions 
thrown by both the Android platform and third party libraries; and (iii) undocumented checked exceptions
 thrown by the Android Platform. Such undocumented exceptions make it difficult, and most of the times infeasible
for the client code to protect against ``unforeseen'' situations that may happen while calling third-party code.
This study provides further insights on such \emph{bug hazards} and the robustness threats  
they impose to Android apps as well as to other systems based on the Java exception model.

%A bug hazard is a circumstance that increases the chance of a bug being present in the software.
\end{abstract}

@@

This study performs a post mortem analysis of the exception stack traces 
included in issues
reported on Android projects hosted in GitHub and Google Code. 
The goal of this study is to investigate whether the reported exception stack traces
 can reveal common \emph{bug hazards} in the exception-related code.  
A \emph{bug hazard}~\cite{binder2000testing}  is a circumstance that increases the 
chance of a bug being present in the software. An example of a bug hazard can 
be a characteristic of  the exception-related code which can increase the likelihood 
of introducing the aforementioned uncaught exceptions.

@@

The remainder of this paper is organized as follows. 
Section~\ref{sec:back} provides the necessary
background on the Android platform and the Java exception model. 
Section~\ref{sec:study} presents the study design. 
Section~\ref{sec:exceptionminer} describes the ExceptionMiner tool we developed to conduct our study.
Section~\ref{sec:result} reports the findings of our study.
Section~\ref{sec:disc} provides a discussion of the wider implications of our results.
Section~\ref{sec:threats} presents the threats to validity associated to this study. 
Finally Section~\ref{sec:rele} describes related work, 
and Section~\ref{sec:conc} concludes the paper and outlines
directions for future work.

@@

@@

@@

The goal of our mining study is to explore to what extent exception stack traces 
contained in issues of Android projects (hosted in GitHub and Google Code), can reveal 
\emph{bug hazards} in the exception-related code of both the applications and the underlying framework. 
As mentioned before, in this context \emph{bug hazards} are the characteristics of exception-related code 
that favor the introduction of failures such as uncaught exceptions. 
To support our investigation, we developed a tool called ExceptionMiner (Section~\ref{sec:exceptionminer})
which extracts the exception stack traces embedded on issues, 
and combines stack trace information with source code and bytecode 
analysis. Moreover, we use manual inspection to augment
 the understanding of stack traces and support further discussions and insights (Section~\ref{sec:manual}).
In this study we explore the domain quantitatively and highlight interesting cases by 
exploring cases qualitatively.

@@

\emph{\textbf{Exception Stack Trace Distiller.}}
This component combines a parser (based on regular expressions) 
and heuristics able to identify and filter exception names and stack traces inline with text. 
This component distills the information that composes a stack trace.
 Some of the attributes extracted from the stack trace are
 the root exception and its signaler, as well as the exception wrappers and their corresponding signalers. 
This component also distills fine grained information of each attribute such as the classes and packages associated to them.
In contrast to existing issue parsing solutions such as Infozilla, our parser
 can discover stack traces mixed with log file information\footnote{In several 
exception stack traces, the exception frames were preceeded by logging information e.g., 
\texttt{03-01 15:55:01.609 (7924): at android.app.ActivityThread.access\$600(ActivityThread\-.java:127)} which could not be detected by existing tools.}.

\emph{\textbf{Exception Type Analysis.}} To support a deeper investigation of the 
stack traces every exception defined on a stack trace needs to be classified according to its type
(e.g. Error, checked Exception or RuntimeException). The module responsible for this analysis 
uses the Design Wizard framework \cite{Brunet09} to inspect the bytecode of the exceptions reported 
on stack traces.  It walks up the type hierarchy of a Java exception until it reaches 
a base exception type. Hence in this study the bytecode analysis was used to discover the type 
of each mined exception when the jar file of such exception was available on the project or 
on a reused  Java library. A specific implementation (based on source code analysis)
 was needed to discover the exception type when the bytecode was not available.
With this module we analyzed all exceptions defined in the Android platform (Version 4.4, API level 19),
which includes all basic Java exceptions that can be thrown during the app execution,
and exceptions thrown by Android core libraries. Moreover, we also analyzed the 
exceptions reported on stack traces that were defined on applications and third-party libraries 
(the tool only analyzed the last version available).

\emph{\textbf{Exception Signaler Analysis.}}
This module is responsible for classifying each signaler according 
to its origin (i.e., Android Application Framework, Android Libcore, Application, Library). 
Table~\ref{tab:signalers} presents the heuristics adopted in this classification.
To conduct this classification, we provide this module with the information
comprising all Java packages that compose: the Android Plaform;
 the Android Libcore; and each analyzed Application. To discover the packages for the first two origins
we can use the Android specification.
To discover the packages for the third origin, the application itself, this module
extracts the manifest files of each Android app, which defines the main packages that the applications consist of.
 If this file is not available, the tool recursively analyzes the 
structure of source-code directories composing the appm filtering out the cases in which the application also includes the source code of reused libraries.
Then, based on this information and using pattern matching 
between the signaler name and the packages, this module identifies 
the origin of the exception signalers.

@@

\subsection{Manual Inspections}
\label{sec:manual}
In our experiments, the output of the ExceptionMiner tool was manually extended
in order to 
(i) support the identification of packages composing the Android platform, 
libs and apps analyzed in this study (as described previously); and (ii)  
identify the type of some exceptions reported in issues 
that were not automatically identified by the ExceptionMiner tool
(because they were defined on previous versions of libraries,
apps and Android Platform). When the exception could not be  
found automatically or manually (because they were defined on a previous version
of the app or lib), we classified the exception as ``Undefined''.  Only 31 exceptions 
remained undefined, which occurred in 60 different exception stack traces (see Table~\ref{tab:typeroottab}).

@@

This section presents the results of the study; this presentation is centered around 
the information distilled from stack traces: (i) the root exceptions (i.e., the exceptions that caused the stack traces);
 (ii) the exception types (i.e, Checked, Runtime, Error, Throwable) and (iii) the exception wrappings. 
Each piece information is then analyzed in detail to 
check whether they can reveal bug harzards on the exception handling code -
related to (i) specific violations of the best practices presented in Section~\ref{sec:best},
or (ii) the general use of exception handling to suport robust development.

\subsection{Can the root exceptions reveal bug harzards?}
After distilling the information available on the exception stack traces, we could find 
the exceptions commonly reported as the root causes of stack traces.
Table \ref{tab:topten} presents a list of the top 10 root exceptions found in the study - 
 ranked by the number of distinct projects on which they were reported. 
This table also shows how many times the signaler of such an exception was a method defined on
the Android platform, the Android libcore, the application itself or a third-party library -
 following the classification presented in Table  \ref{tab:signalers}.

@@

@@

\finding{Almost two thirds of all crashes come from runtime
  exceptions. Most of these originate from the application layer.}

@@

\emph{\textbf{Missing Checked Exceptions on Exception Interfaces.}} 
Our exception stack trace analysis revealed an unexpected bug hazard: a 
checked exception thrown by a native method and not declared on the exception 
interface of these methods signaling them. The native method in question was defined in
 the Android platform, which uses Java Native Invocation (JNI) to access 
native C/C++ code. This exception was thrown by the method getDeclaredMethods defined in java.lang.Class. 
The Java-side declaration of this method does not have any throws clause, 
leading programmers and the compiler to think that no checked exceptions can be thrown.
 However, the C-code implementation did throw a ``checked exception" called NoSuchMethodException, 
violating the declaration. The Java compiler could not detect this violation, because it does 
not perform static exception checking on native methods. This type of bug is hard to diagnose
because the developer usually does not have access to the native implementations. 
Consequently, since it is not expected by the programmer, when such a method throws 
this exception, such an undocumented exception may remain
uncaught and cause the app to crash, or maybe mistakenly handled by subsumption.
The exception stack traces reporting this scenario actually correspond
to a real bug of Android 
Gingerbread version (which still accounts for 13.6\% of devices running Android).
%Among the Android projects on which this exception stack trace was reported we can cite:
%PageTurner (206 stars), ActionBarSherlock (6,041 stars), otto (1,618
%stars).

@@

\finding{%
General catch clauses masking any exception into a general RuntimeException 
is a common practice in the Android Platform; it violates best practice III 
and is considered a bug hazard as it loses contextual information about the exception.
}

@@

On the other hand, the inspection 
also revealed instances of Error wrapping checked exceptions. Such wrappings were 
mostly performed by Java static initializers. If any exception is thrown in the context of a static initializer 
(i.e., static block)  it is converted into an ExceptionInitializerError 
on the point where the class is first used.  Table~\ref{tab:exampeswrap} also illustrates
examples of such wrappings. Although such a wrapping may represent a design decision,
it violates the best practices related to checked exceptions and errors as it mixes the intended handling 
behaviour associated to both types.

@@

@@

\emph{External Validity.} Our work uses the GHTorrent dataset, which although 
comprehensive and extensive is not an exact replica of Github. 
However, the result of this study does not depend on the analysis of
a complete Github dataset. Instead, the goal of our study was to 
pinpoint \emph{bug hazards} on the exception-related code based on 
exception stack trace mining of a subset of projects.
We limited our analysis to a subset of existing open-source Android projects.
We are aware that the exception stack traces reported 
for commercial apps can be different from the ones found in this study, and that
this subset is a small percentage of existing apps.
Such threats are similar to the ones imposed to other empirical studies 
which also use free or open-source Android apps~\cite{Linar13,McDon13,Ruiz12}.
Moreover, several exception stack traces that support the findings of this study
refered to exceptions coming from methods defined on Android Application Framework
and third-party libraries.  Additionaly,  the \emph{bug hazards} observed in this study are due to
characteristics of the Java exception model, which can impose challenges 
the robustness of not only to Android apps but also to other systems
 based on the same exception model.

@@

\textit{Analysis and Use of Stack Trace Information.} Several papers have
investigated the use of stack trace information to support: bug classification
and clustering~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},
fault prediction models~\cite{kim2013predicting}, automated
bug fixing tools~\cite{sinha2009fault} and also the analysis of Android APIs~\cite{kechagia2014}. 
Kim et al.~\cite{kim2011crash} use an
aggregated form of multiple stack traces available in crash reports to detect
duplicate crash reports and to predict if a given crash will be fixed. Dhaliwal
et al.~\cite{dhaliwal2011classifying} proposed a crash grouping approach that
can reduce bug fixing time in approximately 5\%. Wang et
al.~\cite{wang2013improving} propose an approach to identify correlated crash
types and describe a fault localization method to locate and rank files related
to the bug described on a stack trace. Schroter et al.~\cite{schroter2010stack}
conducted an empirical study on the usefulness of stack traces for bug fixing
and showed that developers fixed the bugs faster when failing stack traces were
included on bug issues.  In a similar study, Bettenburg et
al.~\cite{bettenburg2008makes} identify stack traces as the second most stack
trace feature for developers.  Sinha et al.~\cite{sinha2009fault} proposed an
approach that uses stack traces to guide a dataflow analysis for locating and
repairing faults that are caused by the implicitly signaled exceptions. Kim
at al.~\cite{kim2013predicting} proposed an approach to predict the
crash-proneness of methods based information extracted from stack traces and
methods' bytecode operations.  They observed that most of the stack traces were
related to NullPointerException and other implicitly thrown exceptions had
the higher prevalence on the analyzed set of stacks. Kechagia and Spinellis~\cite{kechagia2014}
examined the stack traces embedded on crash reports sent by 1,800 Android apps 
to a crash report management service (i.e., BugSense). They found that 19\% of such stack traces
were caused by unchecked and undocumented exceptions thrown by methods defined on 
Android API (level 15). Our work differs from Kechagia and Spinellis since it is based on
stack traces mined from issues reported by open source developers on GitHub and Googlecode.  
Moreover, our study mapped the origin of each exception 
(i.e., libraries, the Android platform or the application itself) and investigated
the adoption of best practices based on the analysis of stack trace information.
Our work also identified the type of each exception mined from issues
(classifying them as Error, Runtime or Checked) based on the source code
analysis of the exception hierarchy and analized the exception wrappings that can 
happen during the exception propagation.  Such analysis revealed intriging 
\emph{bug hazards} such as the cross-type exception wrappings not discussed in previous works.

@@

\textit{Empirical Studies on Exception Handling Defects.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source code of 32 open-source systems, both for Java and .NET. They
observed that the actions inside handlers were very simple (e.g., logging and present a
message to the user). Coelho et al.~\cite{coelho2008assessing} performed an 
empirical study considering the fault-proneness of aspect-oriented implementations 
for handling exceptions. Two releases of both Java and AspectJ implementations were 
assessed as part of that study. Based on the use of an exception
flow analysis tool, the study revealed that the AOP  refactoring increased the 
number of uncaught exceptions, degrading the robustness of the AO version of every analyzed system.
The main limitation of approaches based on static analysis based approaches are the number of false
positives they can generate, and the problems the faced when dealing with reflection libraries 
and dynamic class loading. Pingyu and Elbaum~\cite{Zhang12} were the first to perform
an empirical investigation of issues, related to exception-related bugs, on Android projects.  
They perform a small scale study on which they manually inspected the issues of 
5 Android applications. They observed that 29\% had to do with poor
exceptional handling code, this empirical study was used to motivate the development of a tool
aiming at amplifying existing tests to validate exception 
handling code associated with external resources. This work inspired ours,
 which automaticaly mined the exception stack traces embedded on issues 
reported on 639 open source Android projects. The goal of our study was
to identify common \emph{bug hazards} on the exception related code that can lead to 
failures such as uncaught exceptions.

\textit{Empirical studies using Android apps.} Ruiz et al.~\cite{Ruiz12}
investigated the degree of reuse across applications in Android Market, the
study showed that almost 23\% of the classes inherited from a base class in the
Android API, and that 217 mobile apps were reused completely by another mobile
app. Pathak et al.~\cite{Patha11} analyzed bug reports and developers
discussions of Android platform and found out that approximately 20\% of
energy-related bugs in Android occurred after an OS update. McDonnell et
al.~\cite{McDon13} conducted a case study of the co-evolution behavior of
Android API and 10 dependent applications using the version history data found
in GitHub. The study found that approximately 25\% of all methods in the client
code used the Android API, and that the methods reusing fast-evolving APIs were
more defect prone then others. Vasquez et al.~\cite{Linar13} analyzed
approximately 7K free Android apps and observed that the last successful apps
used Android APIs that were on average 300\% more change-prone than the APIs
used by the most successful apps. Our work differs from the others as it aims at
distilling stack trace information of bug reports and combine such information
with bytecode analysis, source code analysis and manual inspections
to identify \emph{bug hazards} on the exception handling code of Android apps.
